---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# r6methods

<!-- badges: start -->
[![R-CMD-check](https://github.com/jakubsob/r6methods/workflows/R-CMD-check/badge.svg)](https://github.com/jakubsob/r6methods/actions)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

Generate boilerplate code for R6 classes. Given R6 class create getters and/or setters for selected class fields or use RStudio addins to insert methods straight into class definition.

## Installation

You can install development version from Github using:

``` r
remotes::install_github("jakubsob/r6methods")
```

## Basic usage

Core functionality comes with `make_methods` function.

```{r}
library(r6methods)
library(R6)

Person <- R6Class(
  "Person", 
  public = list(
    name = NULL,
    age = NA,
    initialize = function(name, age = NA) {
      self$name <- name
      self$age <- age
    },
    print = function(...) {
      cat("Person: \n")
      cat("  Name: ", self$name, "\n", sep = "")
      cat("  Age:  ", self$age, "\n", sep = "")
      invisible(self)
    }
  ),
  private = list(
    secret1 = NULL,
    secret2 = NULL
  )
)
```

Create getters and setters for private fields:

```{r}
make_methods(Person, "private", "both")
```

Or only getters:

```{r}
make_methods(Person, "private", "get", add_roxygen = FALSE)
```

You can also create methods for fields of your liking, not only all of private/public:

```{r}
make_methods(Person, c("age", "secret1"), "get", add_roxygen = FALSE)
```

## RStudio addins

Four addins are supplied with the package. They are grouped into 2 families:

  - Generate: makes method strings and prints them to console to be copied to class definition. 
  - Insert: makes method strings and inserts them into class definition.
  
Addins with `gadget` suffix open gadget in RStudio which allows user to have more control over the generated methods.
